\section{Vertex ordering}\label{sec:vo}

\subsection{Shortest Path}

\begin{definition}
  Given a graph $G=\langle V,E \rangle$ and a pair of vertex $(u,u')$,
  a walk $w$ of $(u,u')$ over $G$ is a sequence \((v_i)_{i=0}^{n}\) of vertices such that
  \begin{itemize}
  \item for all $i \in \{0,...,n\}, v_i \in V$,
  \item for all $i \in \{0,...,n-1\}, (v_i,v_{i+1}) \in E$ or $v_i=v_{i+1}$,
  \item $v_0 = u$ and $v_n=u'$.
  \end{itemize}
  $n$ is the lengh of the walk.
\end{definition}
% \begin{definition}  Given a graph $G=\langle V,E \rangle$ and a pair of vertex $(u,u')$,  a path $p$ of $(u,u')$ over $G$ is a walk such such that   for all $i \in \{0,...,n-1\}, (v_i,v_{i+1}) \in E$.  $n$ is the lengh of the path.\end{definition}
\begin{definition}
For a walk $p=((v_i)_{i=0}^{n})$ over $\langle V,E \rangle$ and a vertex $v \in V$,
$v \in p$ if there is an $i\in \{0,...,n\}$ such that $v=v_i$.
\end{definition}
\begin{definition}
For a walk $p=((v_i)_{i=0}^{n})$ over $\langle V,E \rangle$ and an edge $(v,v') \in E$,
$(v,v') \in p$ if there is an $i\in \{0,...,n-1\}$ such that $v=v_i$ and $v'=v_{i+1}$.
\end{definition}
\begin{definition}
  Given a graph $G$ and a pair of vertex $(u,u')$,
  a shortest path $sp$ is a walk of $(u,u')$ over $G$ such that,
  for every walk $p'$ of $(u,u')$ over $G$,
  the lengh of $p'$ is bigger or equal than the lengh of $sp$.
\end{definition}

\subsection{Poset}

Given a graph $G=\langle V,E \rangle$,
an agent is a pair of vertex $(u,v) \in {V\times V}$.

Given a graph $G=\langle V,E \rangle$ and a set of agent $A$,
$sp$ is a mapping over $G$ from an agent $a$ into a shortest path of $a$ over $G$.

Given the tuple $\langle G,A,sp \rangle$,
we can define an partially strictly ordered set $\{S,<\}$ over the tuple as follow:

\begin{enumerate}
  \item $S = \{(v,a) : a \in A, v \in sp(a)\}$
  \\ $(v,a)$ represent the passage of the agent $a$ on the vertex $v$.
  \item For every edge $(v,v') \in E$, if $(v,v') \in sp(a)$, $(v,a)<(v',a)$.\label{succ}
  \item For every vertex $v \in V$, if $v \in sp(a)$ and $v \in sp(a')$
  then $(v,a)<(v,a')$ or $(v,a')<(v,a)$.
  \\ This forbid vertex conflicts.\label{vercon}
  \item For every edge $(v,v') \in E$, if $(v,v') \in sp(a)$ and $(v,v') \in sp(a')$ and $(v,a)<(v,a')$, then $(v',a)<(v',a')$.
  \\ This ensure that, if one agent follow another, he can't pass it.
  \item For every edge $(v,v') \in E$, if $(v,v') \in sp(a)$ and $(v',v) \in sp(a')$ and $(v,a)<(v,a')$, then $(v',a)<(v',a')$
  \\ This forbid edge conflicts.\label{edgcon}
  \item For $a=(u,v)$, for all $a'\in A$, if $u \in sp(a')$, then $(u,a)<(u,a')$.
  \\ This ensure that an agent must leave his starting position for every other agent to pass on it.
  \item For $a=(u,v)$, for all $a'\in A$, if $v \in sp(a')$, then $(v,a')<(v,a)$.
  \\ This ensure that an agent must reach his goal after every other agent passed on it.
  \\ This can be removed if the agent disapear after reaching his target.
\end{enumerate}

Note that a partially strictly ordered set must satisfy irreflexivity and transitivity.

The set $\{S,<\}$ is a correct ordering of the shortest paths.
If no correct ordering exists, the shortests paths are unrepairable with only waits.

Note that there may be redundant rules.

\subsection{Repair}

A repair $\pi$ is a mapping from a shortest path \((p_i)_{i=0}^{n}\) into a walk \((w_i)_{i=0}^{m}\) such that:
\begin{itemize}
  \item for all $i \in \{0,...,n\}$, there is a $j \in \{0,...,m\}$ such that $p_i=w_j$
  \item for all $j \in \{0,...,m\}$, there is an $i \in \{0,...,n\}$ such that $p_i=w_j$
  \item for all $i,i' \in \{0,...,n\}$ with $i<i'$, and all $j,j' \in \{0,...,m\}$
  such that $p_i=w_j$ and $p_{i'}=w_{j'}$, $j<j'$
\end{itemize}

Given the tuple $\langle G,A,sp \rangle$, an ordered set $\{S,<\}$ over this tuple and a repair $\pi$,
we can define a set of walks $\Pi = \{((\pi(sp(a))_i)_{i=0}^{n}) : a\in A\}$ such that:
\begin{itemize}
  \item All walks in $\Pi$ have the same lengh $n$.
%  \item For all $k\in \{0,...,n\}$, for all $\pi \in \Pi$, $v^a_k\in\{v:(v,a)\in S\}$.
%  \item For all $(v,a)\in S,$ there is a $k \in \mathbb{N}$ such that $\pi(a)(k)=(v,a)$.
  \item If $(v,a)<(v',a')$ then for all $k\in \{0,...,n\}$ such that $\pi(sp(a))_k=v$
  and all $k'\in \{0,...,n\}$ such that $\pi(sp(a'))_{k'}=v'$, $ k<k'$.
\end{itemize}

Claim : $\Pi$ is a non-conflicting set of walks.

\subsection{Proof}

\begin{proof}
\begin{itemize}
  %\item Using \ref{succ}, we can affirm that all $\pi \in \Pi$ are a walk.\comment{define walks}
  \item Using \ref{vercon}, we can affirm that For all $k\in \mathbb{N}, \pi_i(k) \not= \pi_j(k)$
  \item For the edge constraints.
  \begin{itemize}
    \item Let's assume we have an edge constraint :
    \begin{itemize}
      \item There is a c such that $\pi_i(c)=v, \pi_i(c+1)=v',\pi_j(c)=v', \pi_i(c+1)=v$
      \item $(v,v') \in sp_i$
      \item $(v',v) \in sp_j$
    \end{itemize}
    \item $(v,v') \in sp_i \rightarrow v_i < v'_i$
    \item $(v',v) \in sp_j \rightarrow v'_j < v_j$
    \item Using \ref{vercon}, $v_i < v_j$ and $v'_j < v'_i$
    \item But this contradict \ref{edgcon}.
  \end{itemize}
\end{itemize}

\end{proof}
